High-Dim Project

### 2014-12-19 highdim-paper/paper.tex

The task of multiclass classification involves the prediction of a class label
$l$ where the number of possible labels is $k>2$. More often than not, the 
original problem is transformed into $k$ binary classification problems, i.e.
$1$--vs.--all classification and positive prediction with the highest 
confidence is selected as the label. This approach has the disadvantage of
having to train $k$ different models.

An alternative formulation, direct multiclass classification, tackles this 
problem directly by solving the following $\operatorname{argmax}$ problem:
$$y_i = \operatorname{argmax}_c W_{:c}^T x_i $$
where $W \in \mathcal{R}^{p \times k}$ is a weight matrix, with $W_{ij}$
corresponding to the $i$-th feature of class $j$. In this paper, we refer
to features as elements in the instance data $x$. A feature in $x$ is
associated with $k$ weights in $W$, one for each class.

@@

Many choices are available for the regularizer $r$. \cite{blondel2013block} uses
the group lasso, where each row in $W$ is a group. The associated regularizer 
then is $r(W) = \lambda\sum_j^p \|W_{j:}\|_2$ where $\lambda$ is a parameter
that adjusts the strength of the regularization.
This has the effect of producing a few rows of non-zero values in $W$;
since each row corresponds to an individual feature, the optimal sparse $W^*$
yields a fast-evaluating decision function, i.e. most features are 
ignored at test time.

To minimize this multi-class classification group lasso objective, coordinate descent method could be used, which iteratively solve a sub-problem with respect to a 
single group. Algorithm~\ref{fig:cooddes} shows a general outline of algorithm that involves
computing the partial gradient with respect to the 
current group $j$, the prox
operator of the L2 norm, and a final line search to identify an appropriate
step size for the current update.

\begin{algorithm}
\caption{coordinate descent among groups}
\label{fig:cooddes}
 \For{$i \gets 1, \ldots, max\;iters $}{
     \For{$j \gets 1, \ldots, p$}{
        Compute gradient $l^\prime(W)_{j:}$\\
        Choose $\mathcal{L}_j$\\
        Compute \\
        $\;\;\;\;V_j = W_{j:} - \frac{1}{\mathcal{L}_j}l^\prime(W)_{j:}$\\
        $\;\;\;\;W_{j:}^* 
          = \operatorname{Prox}_{\frac{\lambda}{\mathcal{L}_j}\|\cdot\|_j}
         (V_j)$\\

@@

One limitation of group lasso is that it assumes that group assignments are
non-overlapping. In some domains, this can be too restrictive an assumption.
For example, in document classification, individual words are used as features.
If we were to construct groupings of these features, we might run into a case
where one word could reasonably be added to several groups. The overlapping or
latent group lasso was introduced to handled such cases.

\cite{obozinski2011group} developed a theoretical justification for the latent group lasso, as well
as its equivalence to a regular group lasso in a higher dimensional space.
Let $\mathcal{G}$ be the set of (possibly overlapping) groups,
where $g \in \mathcal{G}$ is a set of indices of covariates associated with 
that group. 
Let our
data consist of vectors $x_i$ in $p$ dimensions, and let $w$ be the 
corresponding weight vector in $p$ dimensions that we would like to learn.
Finally, define $\operatorname{supp}(v)$ to be the support of $v$, i.e.
the indices of the non-zero elements in $v$.

For each group
$g \in \mathcal{G}$ we associate a latent vector $v^g \in \mathcal{R}^p$ where
$\operatorname{supp}(v^g) = g$, i.e. the nonzero elements in the $v^g$ correspond
to the indices in the group $g$. 
The original weight vector $w$ can be
interpreted as a sum of the latent vectors, or
$w = \sum_{g \in \mathcal{G}} v^g$. 
So now the minimization problem is
$$ \min_{w, v^g} l(w) + \lambda \sum_{g \in \mathcal{G}} d_g \|v^g \|_2 $$
$$\mathrm{s.t.}\;\;\; w = \sum_g v^g$$

When the original problem is regression, 
$w^Tx = \left(\sum_g v^g\right)^Tx = \hat{v}^T \hat{x}$ where 
$\hat{v} = (v^{g})_{g \in \mathcal{G}}$ and
$\hat{x} = \bigoplus_{g \in \mathcal{G} } (x_i)_{i \in g}$, i.e. $\hat{x}$ is
the restrictions of each $g$ stacked on top of each other. $\hat{x}, \hat{v}$ 
have dimension $\sum_{g \in \mathcal{G}} |g|$.
In this formulation, the optimal $\hat{v}^*$ can be found using regular 
non-overlapping group lasso.

@@

The first term is the multiclass squared hinge loss function. We want the dot product of an instance and its feature vector to be as large as possible, and the dot product of this instance and the rest feature vectors to be as small as possible. And as long as their difference is greater then a margin ($1$ in this case), we won't penalize it. In the second term, $W_{g,r}$ means a block of weights in group $g$ and class $m$. The L2-norm regulization is computed and sum up for each block. The $\lambda > 0$ is a parameter controls the trade-off between the hinge loss and the L2-norm regulization.  \\

@@

To create groups, we first clustered the documents using k-means clustering.
For each cluster we formed a feature group by taking the complete set of 
non-zero features for each document in the group.

@@

Given the co-occurence matrix $Z$, a simple greedy algorithm below is used to generates groups for the features. The algorithm generates non-overlapping groups. To generate overlapping groups, skip step 3.

\begin{algorithm}
  \For{$i \gets 0, \ldots, rows(Z) $}{
	   1) Get the indices of the N largest columns from row i\\
       2) Output these indices to a new group\\
       3) Mark all cells in these columns in the matrix Z to be 0.\\
  }
\end{algorithm}

Groups created from this method are more meaningful semantically and more granular. Further granularty can be achieved by couting the frequency of two features in sentence level other than article level.\\

>>>>

The task of multiclass classification involves the prediction of a class label
$l$ where the number of possible labels is $k>2$. More often than not, the 
original problem is transformed into $k$ binary classification problems, i.e.
$1$--vs.--all classification and positive prediction with the highest 
confidence is selected as the label. This approach has the disadvantage of
having to train $k$ different models.\\

An alternative formulation, direct multiclass classification, tackles this 
problem directly by solving the following $\operatorname{argmax}$ problem:
$$y_i = \operatorname{argmax}_c W_{:c}^T x_i $$
where $W \in \mathcal{R}^{p \times k}$ is a weight matrix, with $W_{ij}$
corresponding to the $i$-th feature of class $j$. In this paper, we refer
to features as elements in the instance data $x$. A feature in $x$ is
associated with $k$ weights in $W$, one for each class.\\

@@

Many choices are available for the regularizer $r$. \cite{blondel2013block} uses
the group lasso, where each row in $W$ is a group. The associated regularizer 
then is $r(W) = \lambda\sum_j^p \|W_{j:}\|_2$ where $\lambda$ is a parameter
that adjusts the strength of the regularization.
This has the effect of producing a few rows of non-zero values in $W$;
since each row corresponds to an individual feature, the optimal sparse $W^*$
yields a fast-evaluating decision function, i.e. most features are 
ignored at test time.\\

To minimize this multi-class classification group lasso objective, coordinate descent method could be used, which iteratively solve a sub-problem with respect to a 
single group. Algorithm~\ref{alg:cooddes} shows a general outline of algorithm that involves
computing the partial gradient with respect to the 
current group $j$, the prox
operator of the L2 norm, and a final line search to identify an appropriate
step size for the current update.

\begin{algorithm}
\caption{coordinate descent among groups}
\label{alg:cooddes}
 \For{$i \gets 1, \ldots, max\;iters $}{
     \For{$j \gets 1, \ldots, p$}{
        Compute gradient $l^\prime(W)_{j:}$\\
        Choose $\mathcal{L}_j$\\
        Compute \\
        $\;\;\;\;V_j = W_{j:} - \frac{1}{\mathcal{L}_j}l^\prime(W)_{j:}$\\
        $\;\;\;\;W_{j:}^* 
          = \operatorname{Prox}_{\frac{\lambda}{\mathcal{L}_j}\|\cdot\|_j}
         (V_j)$\\

@@

One limitation of group lasso is that it assumes that group assignments are
non-overlapping. In some domains, this can be too restrictive an assumption.
For example, in document classification, individual words are used as features.
If we were to construct groupings of these features, we might run into a case
where one word could reasonably be added to several groups. The overlapping or
latent group lasso was introduced to handled such cases.\\

\cite{obozinski2011group} developed a theoretical justification for the latent group lasso, as well
as its equivalence to a regular group lasso in a higher dimensional space.
Let $\mathcal{G}$ be the set of (possibly overlapping) groups,
where $g \in \mathcal{G}$ is a set of indices of covariates associated with 
that group. 
Let our
data consist of vectors $x_i$ in $p$ dimensions, and let $w$ be the 
corresponding weight vector in $p$ dimensions that we would like to learn.
Finally, define $\operatorname{supp}(v)$ to be the support of $v$, i.e.
the indices of the non-zero elements in $v$.\\

For each group
$g \in \mathcal{G}$ we associate a latent vector $v^g \in \mathcal{R}^p$ where
$\operatorname{supp}(v^g) = g$, i.e. the nonzero elements in the $v^g$ correspond
to the indices in the group $g$. 
The original weight vector $w$ can be
interpreted as a sum of the latent vectors, or
$w = \sum_{g \in \mathcal{G}} v^g$. 
So now the minimization problem is
$$ \min_{w, v^g} l(w) + \lambda \sum_{g \in \mathcal{G}} d_g \|v^g \|_2 $$
$$\mathrm{s.t.}\;\;\; w = \sum_g v^g$$ 
When the original problem is regression, 
$w^Tx = \left(\sum_g v^g\right)^Tx = \hat{v}^T \hat{x}$ where 
$\hat{v} = (v^{g})_{g \in \mathcal{G}}$ and
$\hat{x} = \bigoplus_{g \in \mathcal{G} } (x_i)_{i \in g}$, i.e. $\hat{x}$ is
the restrictions of each $g$ stacked on top of each other. $\hat{x}, \hat{v}$ 
have dimension $\sum_{g \in \mathcal{G}} |g|$.
In this formulation, the optimal $\hat{v}^*$ can be found using regular 
non-overlapping group lasso.

@@

The first term is the multiclass squared hinge loss function. We want the dot product of an instance and its feature vector to be as large as possible, and the dot product of this instance and the rest feature vectors to be as small as possible. And as long as their difference is greater then a margin ($1$ in this case), we won't penalize it. In the second term, $W_{g,r}$ means a block of weights in group $g$ and class $m$. The L2-norm regulization is computed and sum up for each block. The $\lambda > 0$ is a parameter controls the trade-off between the hinge loss and the L2-norm regulization.

@@

To create groups, we first clustered the documents using k-means clustering.
For each cluster we formed a feature group by taking the complete set of 
non-zero features for each document in the group.\\

@@

Given the co-occurence matrix $Z$, algorithm~\ref{alg:groupgen}  is used to generates groups for the features. The algorithm generates non-overlapping groups. To generate overlapping groups, skip step 3.

\begin{algorithm}
\caption{group generation}
\label{alg:groupgen}
  \For{$i \gets 0, \ldots, rows(Z) $}{
	   1) Get the indices of the N largest columns from row i\\
       2) Output these indices to a new group\\
       3) Mark all cells in these columns in the matrix Z to be 0.\\
  }
\end{algorithm}

Groups created from this method are more meaningful semantically and more granular. Further granularty can be achieved by couting the frequency of two features in sentence level other than article level.
